\documentclass[10pt,letterpaper,final]{moderncv}

% Change this to a color definition from moderncvthemeclassic.sty to change the color
\moderncvstyle{classic}
\moderncvcolor{blue}

%\usepackage[utf8]{inputenc}
\usepackage[margin=.75in]{geometry}
\usepackage{fancyhdr}
\usepackage{url}
%\usepackage[light,math]{kurier}
%\usepackage[default]{lato}
%\usepackage[T1]{fontenc}
%\usepackage{endfloat}
%\usepackage{helvet}
%\renewcommand{\familydefault}{\sfdefault}
%\usepackage{fontspec}
%\usepackage[default,osfigures,scale=0.95]{opensans}
%\usepackage{avant}
%\usepackage[light]{roboto}
%\usepackage[T1]{fontenc}
\usepackage{fontspec}
\setmainfont{Roboto Light}
\usepackage[cmbright]{sfmath}
%\setmainfont{Century Gothic}

\definecolor{Gray}{gray}{0.5}
\pagestyle{fancy}
\rfoot{\color{Gray}\thepage/12}
\lfoot{\color{Gray}Danielle Albers Szafir}
\cfoot{}

% personal data
\name{Danielle}{Albers Szafir}
\title{University of Colorado Boulder}
\subtitle{\small{{{Homepage: {\color{web}\url{http://www.danielleszafir.com/}}}}\\Lab Website: {\color{web}\url{http://cmci.colorado.edu/visualab/}}}}
% \newline {\color{titlecolor}\rule{\textwidth}{.25ex}} \small\\[3pt]{\texttt{{Homepage: {\color{web}\url{http://cs.wisc.edu/~dalbers}}}}}

\extrainfo{315 UCB \\ Department of Information Science  \\  University of Colorado \\ \vspace{12pt} Boulder, CO 80309 \\ \fixedphonesymbol 303.492.8532\\ \emailsymbol danielle.szafir@colorado.edu}
%\phone{608.609.1551 \vspace{2pt}}
%\email{dalbers@cs.wisc.edu}
%\photo[64pt]{Yue_Yu}

%\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}

% the ConTeXt symbol
%\def\ConTeXt{%
%  C%
%  \kern-.0333emo%
%  \kern-.0333emn%
%  \kern-.0667em\TeX%
%  \kern-.0333emt}
\makeatletter
% User command: \genhrulefill
% This time we make it full-fledged! (:-)
%
% SYNOPSIS
%   - \genhrulefill[<base_height>][<thickness>]
%       A rule of thickness <thickness> whose lower edge runs
%       at a height of <base_height> above the baseline of the text.
%   - \genhrulefill[<base_height>]
%       A rule of default thickness (0.4pt) whose lower edge runs
%       at a height of <base_height> above the baseline of the text.
%   - \genhrulefill
%       A rule of default thickness (0.4pt) whose lower edge runs
%       along the baseline of the text.
%   - \genhrulefill*[<thickness>]
%       A rule of thickness <thickness> whose axis is aligned along
%       the math axis.
%   - \genhrulefill*
%       A rule of default thickness (0.4pt) whose axis is aligned along
%       the math axis.
\newcommand*\genhrulefill{%
	\begingroup % paranoid -- it's because we use \@tempdima, etc.
	\@ifstar \@s@genhrulefill \@n@genhrulefill
}

\newcommand*\@n@genhrulefill[1][\z@]{%
	\setlength\@tempdimb{#1}%
	\@x@genhrulefill
}
\newcommand*\@x@genhrulefill[1][.4\p@]{%
	\@tempdima \@tempdimb
	\addtolength\@tempdima{#1}%
	\@genhrulefill
}

\newcommand*\@s@genhrulefill[1][.4\p@]{%
	\setbox\z@ \hbox{$\global \dimen@i \fontdimen22\textfont\tw@$}%
	\setlength\@tempdima{#1}%
	\@tempdimb \dimexpr \dimen@i-\@tempdima/\tw@
	\advance \@tempdima \@tempdimb
	\@genhrulefill
}

\newcommand*\@genhrulefill{%
	\leavevmode
	\leaders \hrule \@height \@tempdima \@depth -\@tempdimb \hfill
	\null
	\endgroup
}
\makeatother
\definecolor{web}{rgb}{0.2,0.2,0.2}
%\definecolor{web}{rgb}{0.5,0.5,0.5}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
	\makecvtitle
\vspace{-30pt}
%\section{\textbf{Research Statement}}
%\cvpubitem{My research bridges data visualization and perception to drive the design of novel systems for analyzing large and complex datasets. I focus on expanding our knowledge of visual  in order to evaluate how visualization design impacts users' abilities to accomplish their analytical goals. Through this process, I derive quantified insight into the role of  perception in interpreting visualizations by anticipating how people will interpret encoded information and use this knowledge to design systems and techniques that overcome scalability and interpretability limitations to tackle new challenges in their data. The resulting visualizations address research problems across a variety of domains, including genomics, proteomics, biochemistry, and the humanities.}
%My goal is to develop an understanding of visual perception in real-world contexts to drive the design of displays for visual exploration and communication. I focus on developing visualization techniques to support graphical comparisons of large and complex datasets with a special emphasis on enhancing the scalability and interpretability of visual displays across a variety of domains.
%I have coordinated multiple efforts aimed at creating a sustained dialog between diverse groups of researchers across the University of Wisconsin-Madison campus to build broader collaborative networks that connect digital practitioners and domain researchers.

%I focus on developing visualization techniques to support graphical comparisons of large and complex datasets with a special emphasis on enhancing the scalability and interpretability of visual displays.

%\subsection{{Research Interests}}
%\cvinterests{}{Data Visualization \vspace{3pt} \newline Perceptual Science \vspace{3pt}\newline Color Science}{}{Computer Graphics and Vision \vspace{3pt}\newline Human-Computer Interaction \vspace{3pt}\newline Machine Learning and Data Mining}
%\cvpubitem{Information Visualization, Computer Graphics, Perceptual Science, Bioinformatics, Human-Computer Interaction, Color Science, Computer Vision, Machine Learning and Data Mining, and Graphic Design. }

%\vspace{3pt}
\section{\textbf{Educational Background}}
\cventry{2009--2015}{{{Ph.D. in Computer Sciences}}}{University of Wisconsin-Madison}{}{}{
	%Studying computer graphics and visualization under Professor Michael Gleicher.\vspace{3pt} \newline
	Minor studies in Perceptual Psychology and Art History\newline{Dissertation}: ``Utilizing Color for Perceptually-Driven Data Visualization'' \newline
	%Conducting research on perceptually-motivated design for scalable data visualization.\vspace{6pt} \newline
	{Dissertation Committee}: Drs. Michael Gleicher, Steven Franconeri, Bilge Mutlu, Robert Roth, \& Kevin Ponto
	%GPA: 3.82/4.00.
}
\vspace{3pt}
\cventry{2009--2011}{{Master of Science in Computer Sciences}}{University of Wisconsin-Madison}{}{}{}
%GPA: 3.77/4.00.}

\vspace{3pt}
\cventry{2007--2009}{{Bachelor of Science in Computer Science}}{University of Washington}{}{}{
	NASA Space Grant Scholar \& four-time Dean's List Member\newline
	Graduated at age 20\newline
	Minor in Mathematics}
%Graduated at age 20.\vspace{3pt} \newline
%GPA: 3.60/4.00.}
%\section{\textbf{Academic Background}}
%\cvitem{Computer Science}{}
%\cvitem{Mathematics}{}

\vspace{-3pt}
\section{\textbf{Employment History}}
%\subsection{{Academia}}
\cventry{2015--Present}{{Assistant Professor \& Founding Faculty Member}}{Department of Information Science, University of Colorado Boulder}{}{}
{
	%Founding faculty member of the Department of Information Science in the College of Media, Communication, and Information. \newline 
	Assistant Professor in the Department of Computer Science \emph{by courtesy}\\
	Assistant Professor in the Center for Research Data \& Digital Scholarship \emph{by courtesy}\\
	Fellow in the Institute of Cognitive Science\\
	Fellow in the ATLAS Institute
}


\vspace{3pt}
\cventry{2010--2015}{{Research Assistant}}{Department of Computer Sciences, University of Wisconsin-Madison}{}{}
{}
%Conducted research on data visualization under Professor Michael Gleicher, with a focus on improving the scalability and interpretability of visual analysis systems.}
% \newline
%	Collaborating with researchers across multiple disciplines to discover and apply novel findings integrating perception, cognition, and visualization to create analytics systems that help advance research in domains ranging from biology to the humanities. }%\vspace{6pt} \newline
%\vspace{3pt}
\cventry{2013}{{Research Intern}}{Tableau Software, Menlo Park, CA}{}{}
{}
%Worked with Vidya Setlur and Maureen Stone investigating interactions of color, task, and data in information visualization.}
%{Worked with Vidya Setlur and Maureen Stone investigating interactions of color, task, and data in visualization. \vspace{6pt} \newline
%Conducted a series of internal and external experiments gauging perceptual effects of color appearance in information visualization, resulting in multiple publications and an on-going collaboration with Tableau Research.}
\cventry{2012}{{Software Development Intern}}{Google, Inc., Madison, WI}{}{}
{}
%Designed and prototyped a web-based bioinformatics data storage and analytics platform leveraging cutting-edge cloud technologies and computational analysis techniques to manage biological data at massive scales.}
%{Designed and prototyped a novel web-based bioinformatics data storage and analytics platform leveraging cutting-edge cloud technologies.\vspace{6pt} \newline
%Worked with developers at several domestic and international offices to interface multiple computational and storage platforms and build a working knowledge of web development best practices and computational analysis techniques to manage data at massive scales.}
\cventry{2009}{{Software Development Intern}}{Boston Scientific, Redmond, WA}{}{}
{}
%Designed an application to automatically derive complete parameter-based test suites for Class 3 medical devices, automating testing for over 3,000 different device parameters.}
\cventry{2008--2009}{Software Development Intern}{Apptio, Bellevue, WA}{}{}
{}
%Served as the first intern for the company, debugging and developing analytic dashboards for predictive business intelligence applications.}

%\vspace{3pt}

\vspace{-6pt}
\section{\textbf{Honors \& Awards}}
\cvpaperentry{2018}{{Forbes 30 Under 30 for Science}, \emph{Forbes Magazine}}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2017}{{Best Paper Award, IEEE VIS Information Visualization}}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2016}{{Doctoral Dissertation Award Honorable Mention, IEEE VGTC VGP}}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2014}{{MERL Best Student Paper Award, IS\&T 22nd Color and Imaging Conference}}{}{}{}{}\vspace{-9pt}
%\cventry{2014}{{Invited Participant}}{Genres of Scholarly Knowledge Production 2014}{}{}{}\vspace{-3pt}
\cvpaperentry{2014}{{Best Presentation Award Honorable Mention, McPherson Eye Research Institute}}{}{}{}{}\vspace{-9pt}
%\cventry{2014}{{Andrew W. Mellon Workshop Grant}}{Digital Humanities Research Network}{}{}{}\vspace{-3pt}
\cvpaperentry{2013}{{Best Poster Award, IEEE VIS Scientific Visualization}}{}{}{}{}\vspace{-9pt}
%\cvpaperentry{2013}{{Doctoral Colloquium}}{IEEE VIS}{}{}{}\vspace{-6pt}
\cvpaperentry{2010--2012}{{BACTER Institute Research Fellow}}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2007--2009}{{NASA Space Grant Scholar}}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2007--2009}{{Dean's List, University of Washington}}{}{}{}{}\vspace{-9pt}

\vspace{-6pt}
\section{\textbf{Publications}}
{Note that $(s)$ indicates student authors under research advisement at the time of publication. Acceptance rates listed where available. Conferences are a primary publication venue in Computer \& Information Sciences. IEEE VIS conference proceedings are published as an issue of \emph{IEEE Transactions on Visualization and Computer Graphics}, and EuroVis conference proceedings are published as an issue of \emph{Computer Graphics Forum}. }\vspace{6pt}

\subsection{Published Works}
\cvpaperentry{Journal Publications}{A. Sarikaya, M. Gleicher, \& \textbf{\textcolor{color5}{D. Albers Szafir}}. \href{http://danielleszafir.com/pubs/summaries-preprint.pdf}{``Design Factors for Summary Visualization in Visual Analytics.''} \emph{Computer Graphics Forum}, 37(3):  145–156, 2018. \newline {\small\emph{> Special Issue: Proceedings of EuroVis 2018. Acceptance Rate: 29\%}}}{}{}{}{}{}

\cvpaperentry{}{\textcolor{color5}{\textbf{D. Albers Szafir}}.\href{http://cmci.colorado.edu/visualab/papers/colordiff_vis2017.pdf}{``Modeling Color Difference for Visualization Design.''} \emph{IEEE Transactions of Visualization and Computer Graphics}, 24(1): 392--401, 2018. \newline {\small\emph{> Special Issue: Proceedings of IEEE VIS 2017. Acceptance Rate: 22.9\%}}\newline{\small\emph{{\textbf{\color{color3}> Best Paper Award (Top paper of 170 submissions)}}}}}{}{}{}{}{} %40 of 170

\cvpaperentry{}{\textcolor{color5}{\textbf{D. Albers Szafir}}, D. Stuffer, Y. Sohail$^{(s)}$, \& M. Gleicher. \href{http://danielleszafir.com/TextDNA.pdf}{``TextDNA: Visualizing Word Usage Patterns with Configurable Colorfields.''} \emph{Computer Graphics Forum}, 35(3): 421--430, 2016. In the Proceedings of the Eurographics Conference on Visualization\newline {\small\emph{> Special Issue: Proceedings of EuroVis 2016. Acceptance Rate: 26\%}}}{}{}{}{}{}

\cvpaperentry{}{\textcolor{color5}{\textbf{D. Albers Szafir}}, S. Haroz, M. Gleicher, \& S. Franconeri. \href{http://jov.arvojournals.org/article.aspx?articleid=2504104}{``Four Types of Ensemble Coding for Data Visualizations.''} \emph{Journal of Vision}, 16(11): 1--19, 2016.  \newline {\small\emph{> 5${th}$ highest scoring Journal of Vision paper on Altmetrics \newline > In Visualizing Data's \emph{Best of the Visualization Web}, May 2017 }}}{}{}{}{}{} %(Impact Factor: 2.34)

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers Szafir}}, A. Sarikaya, \& M. Gleicher. \href{http://ieeexplore.ieee.org/document/7328340/}{``Lightness Constancy in Surface Visualization.''} \emph{IEEE Transactions on Visualization and Computer Graphics}, 22(9): 2107--2121, 2016.}{}{}{}{}{} %(Impact Factor: 1.4)

\cvlistentry{}{A. Sarikaya, \textcolor{color5}{\textbf{D. Albers}}, J. Mitchell, \& M. Gleicher. \href{http://graphics.cs.wisc.edu/Papers/2014/SAMG14/}{``Visualizing Validation of Protein Surface Classifiers.''} \emph{Computer Graphics Forum}, 33(3): 171--180, 2014. \newline {\small\emph{> Special Issue: Proceedings of EuroVis 2014. Acceptance Rate: 25\%}}}{}{}{}{}{}

 \cvlistentry{}{\textcolor{color5}{\textbf{D. Albers}}, C. Dewey, \& M. Gleicher. \href{http://graphics.cs.wisc.edu/Papers/2011/ADG11b/}{``Sequence Surveyor: Leveraging Overview for Scalable Genomic Alignment Visualization.''} \emph{IEEE Transactions of Visualization and Computer Graphics}, 17(5): 2392--2401, 2011. In the Proceedings of the IEEE Information Visualization Conference. \newline {\small\emph{> Acceptance Rate: 25\%}}}{}{}{}{}{}

\cvlistentry{}{M. Gleicher, \textcolor{color5}{\textbf{D. Albers}}, R. Walker, I. Jusufi, C. Hansen, \& J. Roberts. \href{http://graphics.cs.wisc.edu/Papers/2011/GAWJHR11/}{``Visual Comparison for Information Visualization.''} \emph{Information Visualization}, 10(4): 289--309, 2011.}{}{}{}{}{} % (Impact Factor: 0.89)

%\vspace{3pt}
\cvlistentry{{Refereed Conference Papers}}{M. Whitlock$^{(s)}$, E. Hanner, J. Brubaker, S. Kane, \& \textcolor{color5}{\textbf{D. Albers Szafir}}. \href{http://cmci.colorado.edu/visualab/ARDistanceInteractions/vr-2018.pdf}{``Interacting with Distant Objects in Augmented Reality.''} \emph{IEEE Virtual Reality}, 2018. \newline {\small\emph{> Acceptance Rate: 20.6\%}}}{}{}{}{}{}

\cvlistentry{}{C. Diaz$^{(s)}$, M. Walker, \textcolor{color5}{\textbf{D. Albers Szafir}}, \& D. Szafir. \href{http://danielleszafir.com/ar-depth-ismar17.pdf}{``Designing for Depth Perceptions in Augmented Reality.''} In the \emph{Proceedings of the International Symposium on Mixed and Augmented Reality (ISMAR)}, 2017. \newline {\small\emph{> Acceptance Rate: 26\%}}}{}{}{}{}{}  %31 of 117

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers Szafir}}, M. Stone, \& M. Gleicher. \href{http://graphics.cs.wisc.edu/Papers/2014/ASG14/}{``Adapting Color Difference for Design.''} In the \emph{Proceedings of the IS\&T 22nd Color and Imaging Conference}, 2014.  \newline {\small\emph{\textbf{\color{color3}> MERL Best Student Paper Award}}}}{}{}{}{}{}

\cvlistentry{}{M. Stone, \textcolor{color5}{\textbf{D. Albers Szafir}}, \& V. Setlur. \href{http://danielleszafir.com/2014CIC_48_Stone_v3.pdf}{``An Engineering Model for Color Discriminability as a Function of Size.''} In the \emph{Proceedings of the IS\&T 22nd Color and Imaging Conference}, 2014.\newline{\small\emph{> Integrated into D3 as \protect\href{http://gramaz.io/d3-jnd/}{d3-jnd} and Tableau 10}}}{}{}{}{}{}

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers}}, M. Correll, \& M. Gleicher. \href{http://graphics.cs.wisc.edu/Papers/2014/ACG14/}{``Task-Driven Evaluation of Aggregation in Time Series Visualization.''} In the \emph{Proceedings of the 2014 ACM Annual Conference on Human Factors in Computing Systems (CHI)}, 2014. \newline {\small\emph{> Acceptance Rate: 23\%}}}{}{}{}{}{}  

\cvlistentry{}{M. Correll, \textcolor{color5}{\textbf{D. Albers}}, S. Franconeri, \& M. Gleicher. \href{http://graphics.cs.wisc.edu/Papers/2012/CAFG12/}{``Comparing Averages in Time Series Data.''} In the \emph{ Proceedings of the 2012 ACM Annual Conference on Human Factors in Computing Systems (CHI)}, 2012. \newline {\small\emph{> Acceptance Rate: 23\%}}}{}{}{}{}{} 

\cvlistentry{{Magazine Articles}}{\textcolor{color5}{\textbf{D. Albers Szafir}}. \href{}{``The Good, the Bad, and the Biased: Five ways visualizations can mislead (and how to fix them).''} \emph{ACM Interactions}, 2018 (to appear). }{}{}{}{}{}

\cvlistentry{}{C. Fiesler, W. Aspray, L. Barker, J. Brubaker, L. Devendorf, B. Keegan, L. Palen, M. Paul, \textcolor{color5}{\textbf{D. Albers Szafir}}, R. Roque, R. Robinson, A. Voida, \& S. Voida. ``Information Science at CU Boulder.'' \emph{Interactions Magazine.} 24(4), pp. 18-20, 2017. }{}{}{}{}{}

%\vspace{3pt}
\cvlistentry{Refereed Workshops \& Colloquia}{A. Daughton, D. Pruss$^{(s)}$, B. Arnot$^{(s)}$, \textcolor{color5}{\textbf{D. Albers Szafir}} \& M. Paul. ``Characteristics of Behavior Discourse among Twitter Users Discussing Zika.'' \emph{$2^{nd}$ Social Media Mining for Health Applications Workshop \& Shared Task at the 2017 American Medical Informatics Association Annual Symposium.} 2017.}{}{}{}{}{} 
%\footnotetext{* indicates peer-review.}

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers Szafir}} \& D. Szafir.\href{http://cmci.colorado.edu/visualab/papers/16-c4pgv-cogload.pdf}{``Cognitive Load in Visualization: Myths and Misconceptions.''}  \emph{Creation, Curation, Critique and Conditioning of Principles and Guidelines in Visualization (C4PGV).} 2016.}{}{}{}{}{} 

\cvlistentry{}{M. Correll, E. Alexander, \textcolor{color5}{\textbf{D. Albers Szafir}}, A. Sarikaya, \& M. Gleicher. \href{http://graphics.cs.wisc.edu/Papers/2014/CAASG14/24-correll.pdf}{``Navigating Reductionism and Holism in Evaluation.''} \emph{BELIV '14: Beyond Time and Errors---Novel Evaluation Methods for Visualization}, 2014.}{}{}{}{}{} 

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers}}. \href{}{``Perceptually Informed Scalable Sequence Comparison.''} \emph{IEEE VIS Doctoral Colloquium}, 2013.}{}{}{}{}{} 



%\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers Szafir}}. ``Using Graphical Perception to Drive Visualization Design.'' \emph{Visualization Summer Camp.} 2016.}{}{}{}{}{} 

\cvlistentry{Other Workshops}{\textcolor{color5}{\textbf{D. Albers Szafir}} \& C. Fiesler. ``A Crash-Course in P5.'' \emph{NCWIT Aspirations in Computing Colorado Affiliate.} 2017. \newline {\small\emph{> Hands-on workshop for 72 high school women}}}{}{}{}{}{} 

\cvlistentry{}{E. Alexander \& \textcolor{color5}{\textbf{D. Albers Szafir}}. ``D3.js: Javascript for Data Visualization.'' \emph{Second Annual Digital Humanities+Art Symposium: Going Public.} 2015.}{}{}{}{}{} 

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers Szafir}}. \href{http://pages.cs.wisc.edu/~dalbers/DHRN.pdf}{``Thinking with Data.''} \emph{Digital Humanities Research Network}, 2014.}{}{}{}{}{} 


\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers}} \& Michael Gleicher. \href{}{``Seeing Double: Crowdsourced Models of Color Discrimination.''} \emph{Midgraph: Midwest Graphics Workshop}, 2012.}{}{}{}{}{} 

%\subsection{Under Review}
%\cvlistentry{In Preparation}{A. Sarikaya, M. Gleicher, and \textcolor{color5}{\textbf{D. Albers Szafir}}.{``The Design of Visual Summaries.''} \emph{IEEE Transactions of Visualization and Computer Graphics}.}{}{}{}{}{} 
%(Acceptance Rate: 26\%)

%\cvlistentry{}{M. Correll, \textcolor{color5}{\textbf{D. Albers Szafir}}, S. Franconeri, and M. Gleicher. \href{}{``Design Considerations for Visual Aggregation in Time Series Data.''}}{}{}{}{}{}

%\vspace{3pt}
\cvlistentry{{Refereed Abstracts}}{A. Kelly, M. Whitlock$^{(s)}$, B. Nickoloff, A. Lam, \textcolor{color5}{\textbf{D. Albers Szafir}}, \& S. Voida. \href{http://danielleszafir.com/becoming-butterflies.pdf}{``Becoming Butterflies: Interactive Embodiment of the Butterfly Lifecycle.''} \emph{UbiComp Poster Proceedings}, 2017.}{}{}{}{}{} 
 %(Acceptance Rate: 26\%)


\cvlistentry{}{D. Pruss$^{(s)}$, A. Daughton, B. Arnot$^{(s)}$, \textcolor{color5}{\textbf{D. Albers Szafir}, \& M. Paul} {``Content Analysis of Zika Related Tweets.''} \emph{American Public Health Association Annual Conference.} 2017.}{}{}{}{}{} 

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers Szafir}}. {``The Effects of Size and Shape on Color Perception.''} \emph{Vision Science Society Annual Meeting}, 2017.}{}{}{}{}{} 

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers Szafir}} \& M. Gleicher. \href{http://danielleszafir.com/colorposter.pdf}{``Visualization-Aware Color Design.''} \emph{EuroVis Poster Proceedings}, 2016.}{}{}{}{}{} 

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers Szafir}}. ``Considering Connectivity for Visualization Design.'' \emph{Human-Computer Interaction Consortium Conference (HCIC),} 2016.}{}{}{}{}{}

%\cvpubitem{\textcolor{color5}{\textbf{D. Albers Szafir}}.{``Considering Connectivity for Visualization Design.''} \emph{Human Computer Interaction Consortium}, 2016 (under review).}

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers}}, M. Correll, M. Gleicher, \& S. Franconeri. \href{http://graphics.cs.wisc.edu/Papers/2014/ACGF14}{``Ensemble Processing of Color and Shape: Beyond Mean Judgments.''} \emph{Journal of Vision}, 14(9), 2014.}{}{}{}{}{} 

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers}}, A. Sarikaya, \& M. Gleicher. \href{http://graphics.cs.wisc.edu/Papers/2013/ASG13/}{``Lightness Constancy in Surface Visualization.''} \emph{Poster Abstracts of IEEE VIS}, 2013.\newline\emph{\small \textbf{\color{color3}> Best Poster Award, Scientific Visualization Track}} }{}{}{}{}{} 

\cvlistentry{}{A. Sarikaya, \textcolor{color5}{\textbf{D. Albers}}, \& M. Gleicher. \href{http://graphics.cs.wisc.edu/Papers/2013/SAG13/}{``Understanding Performance of Protein Structural Classifiers.''} \emph{Poster Abstracts of IEEE VIS}, 2013.}{}{}{}{}{} 

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers}}, C. Dewey, \& M. Gleicher. \href{http://graphics.cs.wisc.edu/Papers/2011/ADG11a/}{``Sequence Surveyor: Leveraging Overview for Large-Scale Genomic Alignment Visualization.''} \emph{Proceedings of VizBi 2011: Visualizing Biological Data}, 2011.}{}{}{}{}{} 

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers}} \& M. Gleicher. \href{http://graphics.cs.wisc.edu/Papers/2010/AG10a/}{``Poster: Perceptual Principles for Scalable Sequence Alignment
Visualization.''} \emph{2010 IEEE Information Visualization Poster Proceedings}, 2010.}{}{}{}{}{} 

\cvlistentry{}{\textcolor{color5}{\textbf{D. Albers}} \& M. Gleicher. \href{http://graphics.cs.wisc.edu/Papers/2010/AG10/}{``Perceptual Principles for Scalable Sequence Alignment Visualization.''} \emph{Proceedings of the 7th Symposium on Applied Perception in Graphics and Visualization}, 2010.}{}{}{}{}{} 

\cvlistentry{Panel \& Symposium Organization}{C. Nothelfer, Z. Bylinskii, M. Elliott, C. Xiong, \& \textcolor{color5}{\textbf{D. Albers Szafir}}. ``Vision Science Meets Visualization.'' Panel at \emph{IEEE VIS.} Phoenix, AZ, 2017. }{}{}{}{}{}
%Panelists: Ronald Rensink, Steven Franconeri, Karen Schloss, Todd Horowitz, \& Ruth Rosenholtz.
%\vspace{-8pt}

\cvlistentry{}{C. Nothelfer, Z. Bylinskii, M. Elliott, C. Xiong, \& \textcolor{color5}{\textbf{D. Albers Szafir}}. ``Vision and Visualization: Inspiring Novel Research Directions in Vision Science.'' Symposium at \emph{Vision Sciences Society Annual Meeting.} St. Pete's Beach, FL, 2018. }{}{}{}{}{}

\cvlistentry{{Dissertation}}{\textcolor{color5}{\textbf{D. Albers Szafir}}. \href{}{``Utilizing Color for Perceptually-Driven Data Visualization.''} \emph{University of Wisconsin-Madison}, 2015. \newline  {\small\emph{{\textbf{\color{color3}> Honorable Mention, IEEE Visualization \& Graphics Pioneers Best Dissertation Award}}}}}{}{}{}{}{}

%\cvlistentry{Dissertations}{{\textcolor{color5} \textbf{D. Albers Szafir}}. \href{}{``Utilizing Color for Perceptually-Driven Data Visualization.''} \emph{University of Wisconsin-Madison}, 2015.\newline  {\small {\textbf{\color{color3}> Honorable Mention, IEEE Visualization \& Graphics Pioneers Best Dissertation Award}}}}}{}{}{}{}{}
\subsection{Works In-Progress}
\cvpaperentry{Conditionally Accepted}{H. Song$^{(s)}$ \& \textcolor{color5}{\textbf{D. Albers Szafir}}. \href{}{``Where's My Data? Visualizing Missing Values in Time Series Data.''} \emph{IEEE Transactions of Visualization and Computer Graphics}, 2019. In the Proceedings of IEEE VIS 2018. \newline {\small\emph{> Acceptance Rate: 25.7\%}}}{}{}{}{}{}

\cvpaperentry{Under Review}{M. Whitlock$^{(s)}$, K. Wu$^{(s)}$, \& \textcolor{color5}{\textbf{D. Albers Szafir}}. \href{}{``FieldView: Immersive Visualization and Data Fusion for Situated Analysis in the Field.''} \emph{ACM User Interface Software and Technology Symposium}, 2018.}{}{}{}{}{}

\cvpaperentry{}{\textcolor{color5}{\textbf{D. Albers Szafir}}. \href{}{\emph{Towards a Science of Color for Visualization}}, Morgan \& Claypool Synthesis Lectures on Visualization, 2019.}{}{}{}{}{}

\cvpaperentry{}{D. Pruss$^{(s)}$, Y. Fujinuma, M. Paul, A. Daughton, B. Arnot$^{(s)}$, \textcolor{color5}{\textbf{D. Albers Szafir}}, \& J. Boyd-Graber. \href{}{``Zika discourse in the Americas: a multilingual topic analysis of Twitter.''} \emph{PLOS ONE}, 2019.}{}{}{}{}{}

\cvpaperentry{}{J. Muesing$^{(s)}$, L. Burks$^{(s)}$, M. Iuzzolino$^{(s)}$, J. Hatlelid, \textcolor{color5}{\textbf{D. Albers Szafir}}, \& N. Ahmed. \href{}{``Fully Bayesian Human-Machine Data Fusion for Robust Dynamic Target Surveillance and Characterization.''} \emph{AIAA InfoTech @ Aerospace Conference}, 2019.}{}{}{}{}{}

\cvpaperentry{In Revision}{M. Iuzzolino$^{(s)}$, T. Umada$^{(s)}$, N. Ahmed \& \textcolor{color5}{\textbf{D. Albers Szafir}}. \href{}{``In Automation We Trust: Investigating the Role of Uncertainty in Active Learning Systems.''} \emph{Proceedings of the 2019 Conference on Human Factors in Computing Systems}, 2019.}{}{}{}{}{}

\cvpaperentry{In Preparation}{S. Smart$^{(s)}$ \& \textcolor{color5}{\textbf{D. Albers Szafir}}. \href{}{``Measuring the Separability of Shape, Size \& Color in Scatterplots.''} \emph{Proceedings of the 2019 Conference on Human Factors in Computing Systems}, 2019.}{}{}{}{}{}

\cvpaperentry{}{S. Naidu$^{(s)}$ \& \textcolor{color5}{\textbf{D. Albers Szafir}}. \href{}{``Optimizing Highlight Colors in Data Visualization.''} \emph{Proceedings of the 2019 Conference on Human Factors in Computing Systems}, 2019.}{}{}{}{}{}

\cvpaperentry{}{S. Smart$^{(s)}$, K. Wu$^{(s)}$, \& \textcolor{color5}{\textbf{D. Albers Szafir}}. \href{}{``A Data-Driven System for Perceptual Color Encoding Design.''} \emph{IEEE VIS}, 2019.}{}{}{}{}{}

\section{\textbf{Talks}}
\cvlistentry{Invited Talks \& Panels}{Panelist. ``Visualization for Pan- and Meta-genomics'' \emph{Visualization of Biological Data: Crossroads}, Schloss Dagstuhl Seminar Series, Wardern, Germany, 2018.}{}{}{}{}{}

\cvlistentry{}{``Color Perception in Data Visualizations'' \emph{Vision and Visualization: Inspiring novel research directions in vision science}, Vision Sciences Society Annual Meeting, St. Pete's Beach, FL, 2018.}{}{}{}{}{}

\cvlistentry{}{{{Panelist. ``Visualization and Perception Across Scales''} \emph{Learning from the Science of Cognition and Perception}, National Academy of Sciences, Washington, D.C., 2018.}}{}{}{}{}{}

\cvlistentry{}{{{``Scaling up Visualization through Visual Cognition''} \emph{University of Denver}, Denver, CO, 2017.}}{}{}{}{}{}

\cvlistentry{}{{{Panelist, ``Visualization and HPC.''} \emph{Rocky Mountain High Performance Computing Conference}, Boulder, CO, 2017.}}{}{}{}{}{}

\cvlistentry{}{{Panelist, ``Assistant Professors Panel.''} \emph{CRA New Computing Faculty Workshop}, San Diego, CA, 2017.}{}{}{}{}{} 

\cvlistentry{}{{``Facilitating a Dialogue between People \& Data: Lessons in Designing for Big Data.''} \emph{Rocky Mountain Special Libraries Association Mini-Conference}, Denver, CO, 2017.}{}{}{}{}{} 

\cvlistentry{}{{``How do we see data? Ensembles, Constancy, \& Colors.''} \emph{Information Visualization Meet-Up, Vision Science Society Annual Meeting}, St. Pete's Beach, FL, 2017.}{}{}{}{}{} 

\cvlistentry{}{{``Enabling a Dialogue between People \& Data: Lessons in Designing for Big Data.''} \emph{Big Data Bootcamp}, Denver, Colorado, 2016.}{}{}{}{}{} 

\cvlistentry{}{{``Perceptually-Driven Visualization of Complex Data.''} Rochester Institute of Technology, Rochester, New York, 2015.}{}{}{}{}{} 

\cvlistentry{}{{``Perceptually-Driven Visualization of Complex Data.''} \emph{Digital Arts Colloquium}, University of Iowa, Iowa City, Iowa, 2015.}{}{}{}{}{} 

\cvlistentry{}{{``Perceptually-Driven Visualization of Complex Data.''} \emph{Data @ ASU}, Arizona State University, Tempe, Arizona, 2015.}{}{}{}{}{} 

\cvlistentry{}{{``Perceptually-Driven Visualization of Complex Data.''} \emph{Information Science Seminar}, University of Colorado Boulder, Boulder, Colorado, 2015.}{}{}{}{}{} 

\cvlistentry{}{{``Color \& Size.''} \emph{Developer's Seminar,} Tableau Software, Palo Alto, CA.}{}{}{}{}{} 
	% \emph{(joint work w. Maureen Stone and Vidya Setlur)}.}{}{}{}{}{} 

\cvlistentry{}{{``Informing Visualization in the Humanities through Perception and Genomics.''} \emph{Genres of Scholarly Knowledge Production}, Ume{\aa}  University, Ume\aa, Sweden, 2014.}{}{}{}{}{} 

\cvlistentry{Intramural Talks}{{``Visualizing Biological Data.''} \emph{Bioinformatics \& Data Science Supergroup}, University of Colorado Boulder, 2018.}{}{}{}{}{}

\cvlistentry{}{{``Scaling Up Visualization through Visual Cognition.''} \emph{BioFrontiers Seminar}, University of Colorado Boulder, 2018.}{}{}{}{}{}

\cvlistentry{}{{``Scaling Up Visualization through Visual Cognition.''} \emph{Applied Math Seminar}, University of Colorado Boulder, 2017.}{}{}{}{}{}

\cvlistentry{}{{``Scaling Up Visualization through Visual Cognition.''} \emph{Leeds Business Analytics Meet-Up}, University of Colorado Boulder, 2017.}{}{}{}{}{}

\cvlistentry{}{{``DH+Data: How the Digital Humanities shape and are shaped by Data Science.''} \emph{Official Launch of the Center for Research Data and Digital Scholarship}, University of Colorado Boulder, 2017.}{}{}{}{}{}

\cvlistentry{}{{``Information Visualization: Designing with Data.''} \emph{CU-Boulder Data Science Team}, University of Colorado Boulder, 2017.}{}{}{}{}{} 

\cvlistentry{}{{``Perceptually-Driven Information Visualization.''} \emph{Institute of Cognitive Science Seminar}, University of Colorado Boulder, 2015.}{}{}{}{}{} 

\cvlistentry{}{{``An Introduction to Data Visualization.''} \emph{Science Learner's Lunch}, University of Colorado Boulder, 2015.}{}{}{}{}{} 

\cvlistentry{}{{``Perceptually-Driven Information Visualization.''} \emph{CU Libraries Research Seminar}, University of Colorado Boulder, 2015.}{}{}{}{}{} 

\cvlistentry{}{{``Perceptually-Driven Information Visualization.''} \emph{Human-Centered Computing Seminar}, University of Colorado Boulder, 2015.}{}{}{}{}{} 

\cvlistentry{}{{``Insights at a Glance: Visualization at UW-Madison.''} \emph{MERI at a Glance}, McPherson Eye Research Institute, Madison, Wisconsin, 2014.}{}{}{}{}{} 

%%%Guest Lectures are for my eyes only until told otherwise
%\cvlistentry{Guest Lectures}{{``Model-View-Controller.''} \emph{ATLS 5419: Introduction to Virtual Reality}, University of Colorado Boulder, 2016.}{}{}{}{}{} 

%\cvlistentry{}{{``Driving Scalable Visualization with Perception.''} \emph{CSCI 4830: Big Data \& HCI}, University of Colorado Boulder, 2015.}{}{}{}{}{} 

%\cvlistentry{}{{``The Graphics Pipeline.''} \emph{ATLS 5419: Introduction to Virtual Reality}, University of Colorado Boulder, 2015.}{}{}{}{}{} 

%\cvlistentry{}{{``Introduction to Three.js.''} \emph{ATLS 5419: Introduction to Virtual Reality}, University of Colorado Boulder, 2015.}{}{}{}{}{} 

%\cvlistentry{}{{``Interaction in Visualization.''} \emph{CS 838: Visualization}, University of Wisconsin-Madison, Madison, Wisconsin, 2015.}{}{}{}{}{} 

%\cvlistentry{}{{``Color for Computer Graphics.''} \emph{CS 559: Computer Graphics}, University of Wisconsin-Madison, Madison, Wisconsin, 2014.}{}{}{}{}{} 

%\cvlistentry{}{{``Image Compression.''} \emph{CS 559: Computer Graphics}, University of Wisconsin-Madison, Madison, Wisconsin, 2014.}{}{}{}{}{} 

%\cvlistentry{}{{``Perceptually-Driven Sequence Visualization.''} \emph{CS 838: Visualization}, University of Wisconsin-Madison, Madison, Wisconsin, 2012.}{}{}{}{}{} 

\vspace{-12pt}
\section{\textbf{Press Coverage}}
\cvlistentry{}{{``A Snapshot of Current Trends in Visualization.''} \emph{IEEE Computing Now}, 2018.}{}{}{}{}{} \vspace{-6pt}
\cvlistentry{}{{``30-Under-30: Science.''} \emph{Forbes Magazine}, 2017.}{}{}{}{}{} \vspace{-6pt}
\cvlistentry{}{{``Why Visuals are the Most Important Thing in Brand Storytelling.''} \emph{Native Advertising Institute}, 2017.}{}{}{}{}{} \vspace{-6pt}
%\cvlistentry{}{{``A Day in the Lab: Information Science at CU Boulder.''} \emph{ACM Interactions}, 2017.}{}{}{}{}{} 
\cvlistentry{}{{``Grand Challenge expanded and enhanced by new projects.''} \emph{CU Boulder Today}, 2016.}{}{}{}{}{} 

\vspace{-12pt}
%\vspace{3pt}
\section{\textbf{Funding}}
{Total Funded (including Recommended):  \$2,876,934 (Szafir Portion: \$1,028,152). }\vspace{6pt}
%\cvlistentry{Under Review}{Open Remote Sensing Analytics and Collaborative Learning Environment (ORACLE)\newline
%	{\small
%	{\textcolor{color5}{\textbf{Amount:}}} \$2,091,000 \newline
%	{\textcolor{color5}{\textbf{Agency:}}} Air Force SMC-RSX \newline
%	{\textcolor{color5}{\textbf{Role:}}} Key Personnel (PI: S. Palo)\newline
%	{\textcolor{color5}{\textbf{Duration:}}} 06.2018--05.2020}}{}{}{}{}{}

%\cvlistentry{2018--2020}{\$1,795,941: NSF. "BIGDATA: F: Bringing Qualitative Inductive Methodologies to Big Data Analysis.'' (PI, Co-PIs: J. Brubaker, C. Fiesler, \& M. Paul).}{}{}{}{}{} 

%\cvpubitem{\$655,969: NIST PSIAP. ``Data-Mediated Communication with Proximal Robots for Emergency Response,'' 09.2017 -- 05.2020 (PI, Co-PI: D. J. Szafir).}

%\cvlistentry{2017--2018}{CU Outreach Awards. "Virtual Valley: A Cross-Community Interactive.'' (Co-PI, PI: M.L. Mcnamera).}{}{}{}{}{} 


%\cvlistentry{2017--2021}{\$1,400,000: NIH T32 Training Grant. ``IQ Biology: Data Intensive Biomedical Science (DIBS).'' (Senior Personel, PI: Cech).}{}{}{}{}{} 
\subsection{Funded \& Recommended Proposals}
\cvlistentry{Funded Grants}{Collaborative Analyst-Machine Perception for Robust Data Fusion \newline {\small
	{\textcolor{color5}{\textbf{Amount:}}} \$353,936  (Szafir Portion: \$128,102)\newline
	{\textcolor{color5}{\textbf{Agency:}}} Air Force SMC-RSX \newline
	{\textcolor{color5}{\textbf{Role:}}} Co-Principal Investigator (Principal Investigator: N. Ahmed, CU Boulder)\newline
	{\textcolor{color5}{\textbf{Duration:}}} 06.2017--06.2018}}{}{}{}{}{}

\cvlistentry{}{CRII: CHS: Data-Driven Automation of Color Encodings for Data Visualization \newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$174,925  (Szafir Portion: \$174,925)\newline
		{\textcolor{color5}{\textbf{Agency:}}} National Science Foundation \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2017--08.2020}}{}{}{}{}{}

\cvlistentry{}{Computing support for Digital Humanities at CU \newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$46,009 \newline
		{\textcolor{color5}{\textbf{Agency:}}} University of Colorado Boulder Innovative Seed Grant \newline
		{\textcolor{color5}{\textbf{Role:}}} Co-Principal Investigator (Principal Investigator: V. Hulden, CU Boulder)\newline
		{\textcolor{color5}{\textbf{Duration:}}} 06.2017--05.2018}}{}{}{}{}{}


\cvlistentry{}{FieldView: Using Mobile Devices to Blend Data Collection and Analysis for Field Research
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$30,000  (Szafir Portion: \$30,000)\newline
		{\textcolor{color5}{\textbf{Agency:}}} University of Colorado Boulder Innovative Seed Grant \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator (Co-Principal Investigator: Daniel Szafir, ATLAS Institute, CU Boulder)\newline
		{\textcolor{color5}{\textbf{Duration:}}} 07.2016--12.2017}}{}{}{}{}{}
	
\cvlistentry{}{Digital Humanities Research Network\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$7,500 \newline
		{\textcolor{color5}{\textbf{Agency:}}} Andrew W. Mellon Workshop Grant \newline
		{\textcolor{color5}{\textbf{Role:}}} Coordinator (Lead Coordinators: Molly Wright Steenson, Journalism, UW-Madison \& Catherine DeRose, English, UW-Madison) \newline
		%, Coordination Team: Eric Alexander, Joshua Armstrong, Mattie Burkert, Brandee Easter, Jesse Stommel, \& Mark Vareschi)\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2014--08.2015}}{}{}{}{}{}

\cvlistentry{Recommended For Funding}{CHS:​ ​Medium:​ ​Scaling​ ​Qualitative​ ​Inductive​ ​Analysis​ ​through​ ​Computational​ ​Methods \newline {\small
		{\textcolor{color5}{\textbf{Amount:}}} \$1,070,508 (Szafir Portion: \$297,674)\newline
		{\textcolor{color5}{\textbf{Agency:}}} National Science Foundation \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator (Co-Principal Investigators: Jed Brubaker, CU Boulder; Casey Fiesler, CU Boulder; Michael Paul, CU Boulder)\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2018--08.2021}}{}{}{}{}{}
	
\cvlistentry{}{CHS: Medium: Data-Mediated Communication with Proximal Robots for Emergency Response \newline {\small
		{\textcolor{color5}{\textbf{Amount:}}} \$1,194,056 (Szafir Portion: \$397,451)\newline
		{\textcolor{color5}{\textbf{Agency:}}} National Science Foundation \newline
		{\textcolor{color5}{\textbf{Role:}}} Co-Principal Investigator (Principal Investigator: Daniel Szafir, CU Boulder; C. Heckmann, CU Boulder)\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2018--08.2021}}{}{}{}{}{}
	
\cvlistentry{Corporate Gifts}{Information Visualization Hackathon Sponsorship
	\newline
{\small
{\textcolor{color5}{\textbf{Amount:}}} \$10,000  (Szafir Portion: \$10,000)\newline
{\textcolor{color5}{\textbf{Organization:}}} Zayo Group \newline
{\textcolor{color5}{\textbf{Date Received:}}} 01.2017}}{}{}{}{}{}

\cvlistentry{Fellowships \& Travel Grants}{Schloss-Dagstuhl NSF Support Grant 	\newline
{\small
{\textcolor{color5}{\textbf{Sponsor:}}} National Science Foundation \newline
{\textcolor{color5}{\textbf{Date Received:}}} 10.2017}}{}{}{}{}{}

\cvlistentry{}{IEEE VIS Doctoral Colloquium Travel Fellowship	\newline
{\small
{\textcolor{color5}{\textbf{Sponsor:}}} IEEE VIS \newline
{\textcolor{color5}{\textbf{Date Received:}}} 10.2013}}{}{}{}{}{}

\cvlistentry{}{BACTER Research Fellowship	\newline
{\small
{\textcolor{color5}{\textbf{Sponsor:}}} Department of Energy \& the BACTER Institute \newline
{\textcolor{color5}{\textbf{Duration:}}} 06.2010--05.2012}}{}{}{}{}{}
%	. Department of Energy's Institute for Bringing Computational Techniques to Energy Research (BACTER Institute)

\cvlistentry{}{NASA Space Grant Fellowship	\newline
{\small
{\textcolor{color5}{\textbf{Sponsor:}}} NASA \newline
{\textcolor{color5}{\textbf{Duration:}}} 09.2007--06.2009}}{}{}{}{}{} 

\subsection{Proposals Under Review}
\cvlistentry{Federal Grants}{Dynamic Semantic Communications and Reasoning for Collaborative Decision-Making
	 \newline {\small
		{\textcolor{color5}{\textbf{Amount:}}} \$1,566,919 (Szafir Portion: \$414,933) \newline
		{\textcolor{color5}{\textbf{Agency:}}} Office of Naval Research \newline
		{\textcolor{color5}{\textbf{Role:}}} Co-Principal Investigator (Principal Investigator: N. Ahmed, CU Boulder, Co-Principal Investigators: Brad Hayes, CU Boulder, Mark Campbell, Cornell)\newline
		{\textcolor{color5}{\textbf{Duration:}}} 07.2018--06.2022}}{}{}{}{}{}
	
\cvlistentry{}{Forge...
		\newline {\small
			{\textcolor{color5}{\textbf{Amount:}}} \$ (Szafir Portion: \$) \newline
			{\textcolor{color5}{\textbf{Agency:}}} US Air Force SMC \newline
			{\textcolor{color5}{\textbf{Role:}}} Co-Principal Investigator (CU Principal Investigator: D. Massey, CU Boulder; Industry Principal Investigators at Lockheed Martin, Dell, RedHat, Rocket Communication, \& Deloitte)\newline
			{\textcolor{color5}{\textbf{Duration:}}} 09.2018--08.2019}}{}{}{}{}{}

\subsection{Declined Proposals}
\cvlistentry{Federal Grants}{Open Remote sensing Analytics and Collaborative Learning Environment (ORACLE)
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$2,091,000 \newline
		{\textcolor{color5}{\textbf{Agency:}}} US Air Force SMC \newline
		{\textcolor{color5}{\textbf{Role:}}} Co-Principal Investigator (Principal Investigator: S. Palo, CU Boulder; Co-Principal Investigators: B. Possel, CU Boulder; C. Pankratz, CU Boulder; D. Lindholm, CU Boulder;T. Baltzer, CU Boulder; B. Johnson, CU Boulder; T. Hauser, CU Boulder; N. Ahmed, CU Boulder; T. Matsuo, CU Boulder; T. Jones, Digital Globe; M. Bowersox, Digital Globe; B. Legeer, Digital Globe; E. Golden, Digital Globe)})\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2018--08.2020}{}{}{}{}{}
	
\cvlistentry{}{VisualFusion: Combing Data from Robotics and Consumer Devices for New Multimedia
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$50,000 \newline
		{\textcolor{color5}{\textbf{Agency:}}} University of Colorado Boulder Innovative Seed Program \newline
		{\textcolor{color5}{\textbf{Role:}}} Co-Principal Investigator (Principal Investigator: D. Szafir, CU Boulder; Co-Principal Invesitgator: N. Ahmed, CU Boulder)\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2017--08.2018}}{}{}{}{}{}

\cvlistentry{}{NSF II-NEW. The Colorado Hub for Human-Centered Data Science (CODA)
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$999,546 \newline
		{\textcolor{color5}{\textbf{Agency:}}} National Science Foundation \newline
		{\textcolor{color5}{\textbf{Role:}}} Co-Principal Investigator (Principal Investigator: L. Palen, CU Boulder; Co-Principal Investigators: B. Keegan, CU Boulder; A. Voida, CU Boulder; S. Voida, CU Boulder)\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2017--08.2022}}{}{}{}{}{}

\cvlistentry{}{Sloan Research Fellowship
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$60,000 \newline
		{\textcolor{color5}{\textbf{Agency:}}} Sloan Foundation \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2018--08.2021}}{}{}{}{}{}

\cvlistentry{}{Expert-Driven Progressive Summaries of Spatiotemporal Data
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$500,000 \newline
		{\textcolor{color5}{\textbf{Agency:}}} DARPA Young Faculty Awards \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2018--08.2021}}{}{}{}{}{}

\cvlistentry{}{BIGDATA: F: Bringing Qualitative Inductive Methodologies to Big Data Analysis
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$1,795,941 \newline
		{\textcolor{color5}{\textbf{Agency:}}} National Science Foundation \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator (Co-Principal Investigators: J. Brubaker, CU Boulder; C. Fiesler, CU Boulder; M. Paul, CU Boulder)\newline
		{\textcolor{color5}{\textbf{Duration:}}} 01.2018--12.2022}}{}{}{}{}{}

\cvlistentry{}{Data-Mediated Communication with Proximal Robots for Emergency Response
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$655,969 \newline
		{\textcolor{color5}{\textbf{Agency:}}} National Institute of Standards and Technology Public Safety Innovation Program \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator (Co-Principal Investigator: D. Szafir, CU Boulder)\newline
		{\textcolor{color5}{\textbf{Duration:}}} 10.2017--09.2020}}{}{}{}{}{}

\cvlistentry{}{IQ Biology: Data Intensive Biomedical Science (DIBS)
	\newline
	{\small
		%{\textcolor{color5}{\textbf{Amount:}}} {\color{red}\$TBD} \newline
		{\textcolor{color5}{\textbf{Agency:}}} National Institute of Health T32 Training Grant \newline
		{\textcolor{color5}{\textbf{Role:}}} Senior Personnel (Principal Investigator: T. Cech, CU Boulder; Co-Principal Investigators:  R. Dowell, CU Boulder; M. Lladser, CU Boulder)\newline
	%	{\textcolor{color5}{\textbf{Duration:}}} {\color{red}TBD}}}{}{}{}{}{}

\cvlistentry{}{IQ Biology: Data Intensive Biomedical Science (DIBS)
	\newline
	{\small
		%{\textcolor{color5}{\textbf{Amount:}}} {\color{red}\$TBD} \newline
		{\textcolor{color5}{\textbf{Agency:}}} National Science Foundation NRT \newline
		{\textcolor{color5}{\textbf{Role:}}} Senior Personnel (Principal Investigator: M. Lladser, CU Boulder; Co-Principal Investigators:  M. Mozer, CU Boulder; R. Dowell, CU Boulder; T. Cech, CU Boulder; F. Meyer, CU Boulder)\newline
	%	{\textcolor{color5}{\textbf{Duration:}}} {\color{red}TBD}}}{}{}{}{}{}

\cvlistentry{}{PikTrack: Iconographic Tracking Software for Global Visual Studies
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$125,000 \newline
		{\textcolor{color5}{\textbf{Agency:}}} American Council of Learned Societies \newline
		{\textcolor{color5}{\textbf{Role:}}} Co-Principal Investigator (Principal Investigator: L. Gries, CU Boulder; Co-Principal Investigators:  Q. Lv, CU Boulder; B. Gosh, UCSB; D. Thorat, UF; Juan Steyn, NWU; R. Swanepoel, NWU)\newline
		{\textcolor{color5}{\textbf{Duration:}}} 12.2016--05.2018}}{}{}{}{}{}

\cvlistentry{}{Enabling Man-Machine Collaboration in Scalable Analytics
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$361,601 \newline
		{\textcolor{color5}{\textbf{Agency:}}} Air Force Office of Scientific Research Young Investigators Program \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2017--08.2020}}{}{}{}{}{}

\cvlistentry{}{CRII: III: Supporting Observation-Driven Sensemaking for Multiscale Text Analysis
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$153,676 \newline
		{\textcolor{color5}{\textbf{Agency:}}} National Science Foundation \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator\newline
		{\textcolor{color5}{\textbf{Duration:}}} 05.2016--04.2018}}{}{}{}{}{}
	
\cvlistentry{Industry Grants}{Enabling Analyst-Oriented Data Fusion for Public Health Analysis
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$149,843 \newline
		{\textcolor{color5}{\textbf{Agency:}}} Johnson \& Johnson Stem2D \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2017--08.2021}}{}{}{}{}{}

\cvlistentry{}{Crafting Explanatory Narratives from Exploratory Visualization
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$66,115 \newline
		{\textcolor{color5}{\textbf{Agency:}}} Google Faculty Research Awards \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2017--08.2018}}{}{}{}{}{}


\cvlistentry{}{Using Visual Analytics for Improved Machine Classification
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$53,089 \newline
		{\textcolor{color5}{\textbf{Agency:}}} Google Faculty Research Awards \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2016--08.2017}}{}{}{}{}{}

\cvlistentry{}{Increasing Machine Learning Comprehensibility via Visualization
		\newline
		{\small
			{\textcolor{color5}{\textbf{Amount:}}} \$69,146 \newline
			{\textcolor{color5}{\textbf{Agency:}}} Bloomberg Data Science Research Grants \newline
			{\textcolor{color5}{\textbf{Role:}}} Principal Investigator\newline
			{\textcolor{color5}{\textbf{Duration:}}} 09.2016--08.2017}}{}{}{}{}{}
		
\cvlistentry{}{Guiding Effective Information Visualization for Mixed Reality
	\newline
	{\small
		{\textcolor{color5}{\textbf{Amount:}}} \$100,000 \newline
		{\textcolor{color5}{\textbf{Agency:}}} Microsoft Hololens Academic Research \newline
		{\textcolor{color5}{\textbf{Role:}}} Principal Investigator\newline
		{\textcolor{color5}{\textbf{Duration:}}} 09.2016--8.2017}}{}{}{}{}{}


\section{\textbf{Teaching}}
%\cventry{2010--Present}{{Graduate Researcher}}{Department of Computer Sciences}{University of Wisconsin-Madison}{}
%{Conducting research on data visualization under Professor Michael Gleicher, with a focus on improving the scalability and interpretability of visual analysis systems.\vspace{6pt} \newline
%	Collaborating with researchers across multiple disciplines to discover and apply novel findings integrating perception, cognition, and visualization to create analytics systems that help advance research in domains ranging from biology to the humanities. }%\vspace{6pt} \newline
%Research focuses include designing perceptually-motivated scalable visualization techniques for scientific analysis and characterizing visual comparisons over complex datasets.}
%\cventry{2012, 2014, 2015}{{Guest Lecturer}}{Department of Computer Sciences}{University of Wisconsin-Madison}{}
%{Designed lectures on visualization interaction methods and perceptually-motivated visualization design for a combined graduate and undergraduate visualization course.\vspace{6pt}\newline
	%Lectured on  with an emphasis on topics in biological sequence analysis for a graduate visualization course.\vspace{6pt}\newline
%	Redesigned curriculum for color in computer graphics for an undergraduate graphics course.}
\subsection{Courses Taught}
\cventry{Sp. 2018}{INFO 4602/5602: Information Visualization}{{University of Colorado Boulder}}{}{}
{\small {\textcolor{color5}{\textbf{Enrollment:}}}63 students (28 undergraduates and 33 graduates)}\vspace{6pt}
\cventry{F. 2017}{INFO 3401: Information Exploration}{{University of Colorado Boulder}}{}{}
{\small First offering, required course for Information Science\\ {\textcolor{color5}{\textbf{Enrollment:}}}9 students\vspace{6pt}}
%\newline I designed a new hands-on, project-driven course teaching principles of exploratory data analysis and information synthesis. Topics include data collection, fusion, and integrity; qualitative and quantitative analysis techniques; and visual and predictive analytics. The course synthesizes skills from earlier human-computer interaction, statistics, and computing courses to prepare students to solve applied data science problems. }\vspace{6pt}
\cventry{Sp. 2017}{INFO 4602/5602: Information Visualization}{{University of Colorado Boulder}}{}{}
{\small First offering\\ {\textcolor{color5}{\textbf{Enrollment:}}}40 students (22 undergraduates and 18 graduates)}\vspace{6pt}
%\\{\textcolor{color5}{\textbf{Mean Instructor Rating:}}} 5.3/6.0
	%\newline I designed a new project-based course focusing on concepts in information visualization and visual analytics. Topics include the history of visualization, visual perception, web development, and experiment design. Projects in the course enabled direct interaction between the students and local industry partners. The course was delivered to students from a diverse variety of fields, including Information Science, Computer Science, Social Science, Psychology, and Anthropology. }\vspace{6pt}
\cventry{F. 2016}{INFO 1201: Computational Reasoning I}{{University of Colorado Boulder, Co-Instructor: Stephen Voida}}{}{}
{First offering, required course for the College of Media, Communication, and Information\\{\textcolor{color5}{\textbf{Enrollment:}}} 142 undergraduate students }\vspace{6pt}
%\\{\textcolor{color5}{\textbf{Mean Instructor Rating:}}} 5.00/6.00
	%\newline I co-designed a new course teaching principles of computer science and introductory programming. The course satisfies the core technical competency objectives of the new College of Media, Communication, and Information by contextualizing lectures and assignments in fields relevant to students' areas of study, including data analysis and media manipulation. The course was delivered to students from a diverse variety of fields, including Information Science, Media Studies, Communication, Advertising, and Design. }\vspace{6pt}
	
\subsection{Teaching Assistantships}
\cventry{F. 2009}{{CS838: Human-Computer Interaction}}{{University of Wisconsin-Madison}}{}{}
{\small 
	{\textcolor{color5}{\textbf{Enrollment:}}} 8 graduate students\\
	Teaching Assistant for first offering}\vspace{6pt}
	%Assisted students with concepts from the first graduate-level human-computer interaction course offered by the University.
\cventry{F. 2009}{CS 302: Introduction to Programming}{\small {University of Wisconsin-Madison}}{}{}
{\small
	{\textcolor{color5}{\textbf{Enrollment:}}} 110 undergraduate students }\vspace{3pt}
	%\\{\textcolor{color5}{\textbf{Mean Instructor Rating:}}} 4.58/5.00}\vspace{3pt}
	%Supervised four semester-long hands-on programming sessions and worked one-on-one with students in an introductory programming course (mean instructor rating: 4.58/5.00).
	 %\vspace{6pt} \newline
%Worked one-on-one with students to enforce course concepts in weekly office hours. }
%\vspace{-9pt}
%\cventry{2008--2009}{{Mathematics and English Instructor}}{\emph{Kumon of Redmond}}{}{}{}
	%Instructed K-12 and adult students in concepts from mathematics and English, working with small groups of students progressing through individualized curricula. %\vspace{6pt} \newline
	%Served as the principle tutor for advanced mathematics and assisted with course planning and student progress assessment.
\subsection{Guest Lectures}
	\cvlistentry{Sp. 2018}{{``Data Visualization.''} \emph{INFO 1121: Introduction to Information Science: Designing Interactions}}{}{}{}{}{} \vspace{-6pt}
	
	\cvlistentry{Sp. 2018}{{``Visual Communication.''} \emph{MUSM 5011: Introduction to Museum Studies}}{}{}{}{}{} \vspace{-6pt}

	\cvlistentry{F. 2017}{{``Expectation Maximization.''} \emph{INFO 4604/5604: Applied Machine Learning}}{}{}{}{}{} \vspace{-6pt}
	
	\cvlistentry{F. 2017}{{``Visual Data Mining.''} \emph{CSCI 4502/5502: Data Mining}}{}{}{}{}{}  \vspace{-6pt}

	\cvlistentry{F. 2017}{{``Meet the Faculty.''} \emph{INFO 7000: Introduction to Ph.D. Studies}}{}{}{}{}{} \vspace{-6pt}

	\cvlistentry{F. 2017}{{``Meet the Faculty.''} \emph{CSCI 6000: Introduction to the Computer Science Ph.D. Program}}{}{}{}{}{} \vspace{-6pt}

	\cvlistentry{Sp. 2016}{{``Technology \& Museum Studies.''} \emph{MUSM 5011: Introduction to Museum Studies}}{}{}{}{}{} \vspace{-6pt}
	
	\cvlistentry{F. 2016}{{``Early Career Faculty Panel.''} \emph{CSCI 6000: Introduction to the Computer Science Ph.D. Program}}{}{}{}{}{} \vspace{-6pt}

	\cvlistentry{F. 2016}{{``Model-View-Controller.''} \emph{ATLS 5419: Introduction to Virtual Reality}}{}{}{}{}{} \vspace{-6pt}
	
	\cvlistentry{Sp. 2016}{{``Introduction to Visualization.''} \emph{CMCI 1020: Concepts \& Creativity}}{}{}{}{}{} \vspace{-6pt}
	
	\cvlistentry{F. 2015}{{``Driving Scalable Visualization with Perception.''} \emph{CSCI 4830: Big Data \& HCI}}{}{}{}{}{} \vspace{-6pt}
	
	\cvlistentry{F. 2015}{{``The Graphics Pipeline.''} \emph{ATLS 5419: Introduction to Virtual Reality}}{}{}{}{}{} \vspace{-6pt}
	
	\cvlistentry{F. 2015}{{``Introduction to Three.js.''} \emph{ATLS 5419: Introduction to Virtual Reality}}{}{}{}{}{} \vspace{-6pt}
	
	\cvlistentry{Sp. 2015}{{``Interaction in Visualization.''} \emph{CS 838: Visualization}}{}{}{}{}{} \vspace{-6pt}
	
	\cvlistentry{F. 2014}{{``Color for Computer Graphics.''} \emph{CS 559: Computer Graphics}}{}{}{}{}{} \vspace{-6pt}
	
	\cvlistentry{F. 2014}{{``Image Compression.''} \emph{CS 559: Computer Graphics}}{}{}{}{}{} \vspace{-6pt}
	
	\cvlistentry{Sp. 2012}{{``Perceptually-Driven Sequence Visualization.''} \emph{CS 838: Visualization}}{}{}{}{}{} \vspace{-6pt}

\vspace{-6pt}
\section{\textbf{Mentorship \& Advising}}
\vspace{-3pt}
\subsection{{Ph.D. Direct Advisees}}
\cvlistentry{2017--Present}{\textcolor{color5}{\textbf{Stephen Smart}}, Computer Science, University of Colorado Boulder}{}{}{}{} \vspace{-6pt}
\cvlistentry{2016--Present}{\textcolor{color5}{\textbf{Matthew Whitlock}}, Computer Science, University of Colorado Boulder}{}{}{}{} \vspace{-6pt}
\cvlistentry{2016--Present}{\textcolor{color5}{\textbf{Michael Iuzzolino}}, Computer Science, University of Colorado Boulder \newline \emph{\small > Co-advised with Daniel Szafir}}{}{}{}{} \vspace{-3pt}


\subsection{{Ph.D. Thesis Committee Membership}}
\cvlistentry{2017}{\textcolor{color5}{\textbf{Reem Albaghli}}, Ph.D. Thesis, Department of Computer Science, University of Colorado Boulder \newline {
		\emph{A Framework to Design and Evaluate Wearable Interactive Systems for Health}, Advisor: Ken Anderson}
}{}{}{}{}\vspace{-12pt}
\cvlistentry{2017}{\textcolor{color5}{\textbf{Brett Roads}}, Ph.D. Thesis, Department of Computer Science, University of Colorado Boulder \newline {
	\emph{The Design of Efficient Training and Decision-Support Systems for Visual Categorization}, Advisor: Michael Mozer}
}{}{}{}{}\vspace{-3pt}
\cvlistentry{2015}{\textcolor{color5}{\textbf{Khalid Alharbi}}, Ph.D. Thesis, Department of Computer Science, University of Colorado Boulder \ \newline{
	\emph{A Deep and Longitudinal Approach to Mining Mobile Applications}, Advisor: Tom Yeh
	}
	}{}{}{}{}

\subsection{{Ph.D. Qualifying Committee Membership}}
	\cvlistentry{2018}{\textcolor{color5}{\textbf{Ashlynn Daughton}}, Department of Information Science, University of Colorado Boulder
	}{}{}{}{}\vspace{-6pt}
\cvlistentry{2018}{\textcolor{color5}{\textbf{Xiaolei Huang}}, Department of Information Science, University of Colorado Boulder
}{}{}{}{}
	
\vspace{-6pt}
\subsection{{Masters Students}}
\cvlistentry{2018--Present}{\textcolor{color5}{\textbf{Sreesha Nath}}, Computer Science, University of Colorado Boulder }{}{}{}{} \vspace{-6pt}
\cvlistentry{2018--Present}{\textcolor{color5}{\textbf{Supriya Naidu}}, Computer Science, University of Colorado Boulder }{}{}{}{} \vspace{-6pt}
\cvlistentry{2017--Present}{\textcolor{color5}{\textbf{Keke Wu}}, Creative Technologies, University of Colorado Boulder }{}{}{}{} \vspace{-6pt}
\cvlistentry{2017--2018}{\textcolor{color5}{\textbf{Justin Chin}}, Computer Science, University of Colorado Boulder }{}{}{}{} \vspace{-6pt}
\cvlistentry{2017--2018}{\textcolor{color5}{\textbf{Hayeong Song}}, Computer Science, University of Colorado Boulder \newline \emph{\small > Thesis: Measuring the Role of Visualization on Missing Values in Time Series Data\newline > Now a Ph.D. student at Georgia Tech} }{}{}{}{} \vspace{-3pt} %\newline \emph{An Accessible Analytics Pipeline for Data Fusion in Social Media}
\cvlistentry{2016--2018}{\textcolor{color5}{\textbf{Pratima Sherkane}}, Computer Science, University of Colorado Boulder }{}{}{}{} \vspace{-6pt}%\newline \emph{Predictive Decision-Making with Time Series Visualization}
\cvlistentry{2016--2018}{\textcolor{color5}{\textbf{Hemang Bansal}}, Computer Science, University of Colorado Boulder \newline \emph{\small > Now at CenturyLink}}{}{}{}{} \vspace{-3pt}%\newline \emph{Model Design Structures in Color Encodings}
\cvlistentry{2016--2017}{\textcolor{color5}{\textbf{Dasha Pruss}}, Information Science, University of Colorado Boulder \newline \emph{\small > co-advised with Michael Paul\newline> Now at the University of Pittsburgh Philosophy of Science Ph.D. Program} }{}{}{}{}\vspace{-3pt}
\cvlistentry{2017}{\textcolor{color5}{\textbf{Mridula Natarjan}}, Computer Science, University of Colorado Boulder }{}{}{}{}\vspace{-6pt} %\newline \emph{Tracing the Discussions of Zika in Social Media}
\cvlistentry{2016--2017}{\textcolor{color5}{\textbf{Praveen Devaraj}}, Computer Science, University of Colorado Boulder}{}{}{}{} \vspace{-6pt}% \newline \emph{Using Visualization to Enable Human-Machine Collaboration}
\cvlistentry{2016--2017}{\textcolor{color5}{\textbf{Yogitha Madhasu}}, Computer Science, University of Colorado Boulder \newline \emph{\small > Now at VISA} }{}{}{}{} \vspace{-3pt}%\newline \emph{Visual Analytics for Inductive Scholarship.}}
\cvlistentry{2016}{\textcolor{color5}{\textbf{Shashidhar Prabhu}}, Computer Science, University of Colorado Boulder }{}{}{}{} %\newline \emph{Visualizing Data in the Internet of Things}

%\vspace{3pt}
%\subsection{M.S. Thesis Committee Membership}
%\cvlistentry{2016}{\textcolor{color5}{\textbf{Justin Chin}}, M.S. Thesis, Advisor: Gregor Henze \newline
%	\emph{Virtual Reality Visualizations for Building Energy Management} \newline
%	Department of Civil Engineering, University of Colorado Boulder
%}{}{}{}{}

\vspace{-6pt}
\subsection{{Undergraduate Students}}
\cvlistentry{2017--2018}{\textcolor{color5}{\textbf{Michael Xiao}}, Computer Science, University of Colorado Boulder\newline \emph{\small > Co-advised with J. Brubaker \newline > 2017-2018 Discovery Learning Assistant}}{}{}{}{} \vspace{-3pt} 
\cvlistentry{2017--2018}{\textcolor{color5}{\textbf{Ian Fawaz}}, Computer Science, University of Colorado Boulder\newline \emph{\small > Co-advised with J. Brubaker \newline > 2017-2018 Discovery Learning Assistant}}{}{}{}{} \vspace{-3pt} 
\cvlistentry{2016--2018}{\textcolor{color5}{\textbf{Tetsumichi Umada}}, Computer Science, University of Colorado Boulder\newline \emph{\small > Now in the Computer Science Master's Program at CU Boulder}}{}{}{}{} \vspace{-3pt} % \newline \emph{Using Visualization to Enable Human-Machine Collaboration
\cvlistentry{2017}{\textcolor{color5}{\textbf{Wil Braun}}, Computer Science, University of Colorado Boulder}{}{}{}{} \vspace{-6pt} 
% \newline \emph{Statistically Controlled Synthetic Data Generation
\cvlistentry{2017}{\textcolor{color5}{\textbf{Girishkumar Ramkumar}}, Computer Science, University of Colorado Boulder}{}{}{}{} \vspace{-6pt} % \newline \emph{Visual Analytics for Inductive Scholarship
\cvlistentry{2016--2017}{\textcolor{color5}{\textbf{Ryan Mustari}}, Applied Mathematics \& Economics, University of Colorado Boulder \newline \emph{\small > 2016-2017 UROP Recipient}}{}{}{}{} \vspace{-3pt} %
\cvlistentry{2016}{\textcolor{color5}{\textbf{Alex Thompson}}, Computer Science, University of Colorado Boulder }{}{}{}{} \vspace{-6pt} %\newline \emph{Visualizing Data in Augmented Reality}
\cvlistentry{2016}{\textcolor{color5}{\textbf{Connor Mcguinness}}, Computer Science, University of Colorado Boulder \newline \emph{\small > Now at Uber} }{}{}{}{} \vspace{-3pt}%\newline \emph{Color Encodings for Ordinal Data}
\cvlistentry{2015--2016}{\textcolor{color5}{\textbf{Yusef Suhail}}, Computer Science, University of Wisconsin-Madison }{}{}{}{} \vspace{-6pt} %\newline \emph{Web-based N-Grams Visualization with TextDNA}
\cvlistentry{2014}{\textcolor{color5}{\textbf{Andrew Hermus}}, Computer Science, University of Wisconsin-Madison \newline \emph{\small > Co-supervised with Eric Alexander}\newline \emph{\small > Now at Microsoft}}{}{}{}{} \vspace{-3pt} % \newline \emph{Scalable Visualization for Text Analytics} 
\cvlistentry{2013}{\textcolor{color5}{\textbf{Benjamin Reddersen}}, Computer Science, University of Wisconsin-Madison}{}{}{}{} % \newline \emph{Rendering Techniques for Molecular Surface Visualization}

%\vspace{3pt}
%\subsection{{Industry}}
%\cventry{2013}{{Research Intern}}{Tableau Software}{Menlo Park, CA}{}
%{Worked with Vidya Setlur and Maureen Stone investigating interactions of color, task, and data in information visualization, resulting in multiple publications and an on-going collaboration with Tableau Research.}
%%{Worked with Vidya Setlur and Maureen Stone investigating interactions of color, task, and data in visualization. \vspace{6pt} \newline
%%Conducted a series of internal and external experiments gauging perceptual effects of color appearance in information visualization, resulting in multiple publications and an on-going collaboration with Tableau Research.}
%\cventry{2012}{{Software Development Intern}}{Google}{Madison, WI}{}
%{Designed and prototyped a web-based bioinformatics data storage and analytics platform leveraging cutting-edge cloud technologies and computational analysis techniques to manage biological data at massive scales.}
%%{Designed and prototyped a novel web-based bioinformatics data storage and analytics platform leveraging cutting-edge cloud technologies.\vspace{6pt} \newline
%%Worked with developers at several domestic and international offices to interface multiple computational and storage platforms and build a working knowledge of web development best practices and computational analysis techniques to manage data at massive scales.}
%\cventry{2009}{{Software Development Intern}}{Boston Scientific, CRM}{Redmond, WA}{}
%{Designed an application to automatically derive complete parameter-based test suites for Class 3 medical devices, automating testing for over 3,000 different device parameters.}
%\cventry{2008--2009}{Software Development Intern}{Apptio}{Bellevue, WA}{}
%{Served as the first intern for the company, debugging and developing analytic dashboards for predictive business intelligence applications.
%}

%\vspace{3pt}
\section{\textbf{Professional Activities \& Service}}
\subsection{{Outreach}}
\cvpaperentry{2016--present} {Aspirations in Computing Colorado Affiliate Committee, National Center for Women in Technology}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2010--2015}{{ACM-W Mentor}, Department of Computer Sciences, University of Wisconsin-Madison}{}{}{}{}\vspace{-9pt}
%Mentored 15 undergraduate women in computer sciences with interests in computer graphics and visualization.
\cvpaperentry{2009}{{Majors Fair Representative}, Department of Computer Sciences, University of Wisconsin-Madison}{}{}{}{}\vspace{-9pt}
%Provided information about computer science and gave demos of current undergraduate research projects to incoming freshmen.
\cvpaperentry{2009}{{Department Guide}, Department of Computer Sciences, University of Washington}{}{}{}{}
%Guided elementary school students through a series of hands-on activities and presentations from computer science researchers.


\vspace{-6pt}
\subsection{Departmental Service}
\cvpaperentry{2015--present}{{Graduate Program Committee, Department of Information Science}}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2016--present}{{Curriculum Committee: Computing Core, Department of Information Science}}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2015--2018}{{Graduate Program Committee, Department of Computer Science}}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2018}{Faculty Search Commitee, Department of Information Science}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2016 - 2017}{External Programs Coordinator, Department of Information Science}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2015}{{Curriculum Creation Committee, Department of Information Science}}{\newline{\small\emph{> Designed novel undergraduate and graduate curricula in Information Science, focusing on the intersection of data, people, and technology. These curricula blend topics from computer science, social science, and data science, emphasizing broad application of these skills across different domains. }}}{}{}{}\vspace{-6pt}
\cvpaperentry{2015}{{Faculty Search Committee, Department of Information Science}}{}{}{}{}

\vspace{-6pt}
\subsection{College Service}
\cvpaperentry{2015-2016}{{Community and Diversity Committee}, College of Media, Communication, and Information, University of Colorado Boulder}{}{}{}{}

\vspace{-6pt}
\subsection{{University Service}}
\cvpaperentry{2017 - present}{Advisory Board Member, Center for Research Data \& Digital Scholarship (CRDDS)}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2017 - present}{Digital Humanities Certificate Committee Member}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2018}{Visualization Contest Judge, Center for Research Data \& Digital Scholarship (CRDDS)}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2016 - 2017}{Co-Chair, Digital Humanities Certificate Committee}{\newline{\small\emph{> Resulted in creation of a new interdisciplinary graduate certificate program}}}{}{}{}\vspace{-6pt}
\cvpaperentry{2016}{Faculty Search Committee, Leeds School of Business}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2015-2016}{{Research Data Advisory Committee}}{}{}{}{}\vspace{-9pt}
\cvpaperentry{2014--2015}{{Digital Humanities Research Network Founding Member \& Coordinator, University of Wisconsin-Madison}}{}{}{}{}\vspace{-9pt}
%{Coordinating bi-weekly meetings for a Mellon-funded working group on the digital humanities, bringing together researchers from over a dozen departments at the University of Wisconsin-Madison.}
%\cventry{2012--2015}{{Visualization Reading Group Founder \& Coordinator}}{University of Wisconsin-Madison}{}{}{}
%Created a weekly campus-wide discussion group for topics in visualization integrating researchers from a variety of discliplines.} 
%from computer science, English, journalism, environmental sciences, human ecology, and cartography.}
\cvpaperentry{2015}{Organizing Committee Member, University of Wisconsin-Madison Digital Humanities+Art Symposium}{}{}{}{}

\vspace{-6pt}
\subsection{{Program Committee Membership}}
\cvlistentry{2018--present}{ACM Conference on Human Factors in Computing Systems}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2018--present}{Information+}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2017--present}{Human Computer Interaction Consortium}{}{\newline \emph{> Colorado Governing Board Representative}}{}{}{}\vspace{-6pt}
\cvlistentry{2017--present}{European Conference on Visualization State-of-the-Art Reports (EuroVis STARs)}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2017--present}{IEEE VIS Information Visualization}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2017}{VDS: Visual Data Science Symposium}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2017}{VISSOFT: IEEE Working Conference on Software Visualization}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2016--2017}{LDAV: IEEE Symposium on Large Data Analysis and Visualization}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2014--2016}{BioVis: Symposium on Biological Data Visualization}{}{}{}{}{}

\vspace{-6pt}
\subsection{Grant Referee Service}
\cvlistentry{2018}{Reviewer, Research Innovation Office Innovative Seed Grants}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2017}{Reviewer Ad Hoc, Icelandic Research Foundation}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2017}{Reviewer, National Science Foundation}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2015, 2017}{Reviewer Ad Hoc, National Science Foundation}{}{}{}{}{}

\vspace{-6pt}
\subsection{Journal \& Conference Referee Service}
\cvlistentry{2018}{Science Advances}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2018}{IEEE TBD: Transactions on Big Data}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2016--2018}{EuroVis: Eurographics Conference on Visualization}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2017--2018}{IEEE TVCG: IEEE Transactions on Visualization and Computer Graphics}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2016--2018}{ACM CHI: ACM Conference on Human Factors in Computing Systems \newline \small{{{\emph{> Special Recognition:}}} 2016}}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2013--2018}{IEEE Information Visualization \newline \small{{{\emph{> Special Recognition:}}} 2014, 2015}}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2016--2017}{IEEE LDAV: IEEE Symposium on Large Data Analysis and Visualization}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2015--2017}{IEEE VAST: Visual Analytics Science and Technology}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2013--2016}{BioVis: Symposium on Biological Data Visualization}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2016}{IEEE RO-MAN: IEEE Conference on Robot and Human Interactive Communication}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2014, 2016}{BMC Medical Informatics and Decision Making}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2015--2016}{Informatics}{}{}{}{}{}\vspace{-6pt}
\cvlistentry{2015}{Cartography and Geographic Information Science)}{}{}{}{}{}

%\vspace{-12pt}
%\subsection{{Other Experience}}
%\cventry{2008--2009}{{Ice Hockey Official}}{Puget Sound Hockey Officials Association}{}{}{}
%\cventry{2005--2009}{{Ice Hockey Official}}{Cascade Hockey Officiating Association}{}{}{}

%\section{\textbf{Computing Languages}}
%\cvsubentrynocomma{Programming:}{}{}{JavaScript, Java, Python, C\#, C++, C, SQL, ActionScript, XML, HTML, PHP, Ruby, Haskell, Scheme}{}{}
%\cvsubentrynocomma{Scientific:}{}{}{JMP, Matlab, R}{}{}
\vspace{-6pt}
\subsection{{Professional \& Academic Memberships}}
%\cvmembers{}{ACM Student Member \vspace{3pt}\\ Sigma Alpha Lambda Honor Society}{}{IEEE Student Member \vspace{3pt}\\ Phi Theta Kappa International Honor Society} %international
\cvlistentry{2018--Present}{Sigma Xi Full Member}{}{}{}{}\vspace{-6pt}
\cvlistentry{2010--Present}{ACM Member}{}{}{}{}\vspace{-6pt}
\cvlistentry{2010--Present}{IEEE Member}{}{}{}{}\vspace{-6pt}
\cvlistentry{2015, 2017--Present}{Vision Science Society Member}{}{}{}{}\vspace{-6pt}
\cvlistentry{2008--Present}{Sigma Alpha Lambda Honor Society Member}{}{}{}{}\vspace{-6pt}
\cvlistentry{2008--Present}{Phi Theta Kappa International Honor Society Member}{}{}{}{}\vspace{-6pt}
\cvlistentry{2014--2015}{IS\&T Student Member}{}{}{}{}\vspace{-6pt}
\cvlistentry{2012--2015}{WHCI+D Member}{}{}{}{}\vspace{-6pt}

%\vspace{-6pt}
%\subsection{{Volunteer Positions}}
%\cvlistentry{2009--2014}{{Web Manager}, University of Wisconsin-Madison Women's Hockey Club}{}{}{}{} \vspace{-6pt}
%\cvlistentry{2011--2012}{{Assistant Practice Coach}, Wisconsin Timberwolves Special Needs Hockey Team}{}{}{}{} \vspace{-6pt}
%\cvlistentry{2010}{{GRE Tutor}, University of Wisconsin-Madison}{}{}{}{} \vspace{-6pt}
%\cvlistentry{2007--2008}{{Ice Hockey Officiating Mentor}, Cascade Hockey Officiating Association}{}{}{}{}

\vspace*{\fill}
\color{color3}
\genhrulefill*[.25ex]\quad {\large Professional references available upon request.} \quad\genhrulefill*[.25ex]

%\subsection{Professional references available upon request}
%\section{\textbf{Professional References}}
%\cvmembers{}{\textcolor{color5}{\textbf{Michael Gleicher, Professor}}\\ Department of Computer Sciences \\ University of Wisconsin-Madison \\ gleicher@cs.wisc.edu \vspace{9pt} \\
%\textcolor{color5}{\textbf{Maureen Stone, Research Scientist}}\\ Tableau Software \\  mstone@tableausoftware.com}{}{\textcolor{color5}{\textbf{Steven Franconeri, Associate Professor}}\\ Department of Psychology \\ Northwestern University  \\ franconeri@northwestern.edu \vspace{9pt} \\ 
%\textcolor{color5}{\textbf{Kevin Ponto, Assistant Professor}}\\ Design Studies Department \\ University of Wisconsin-Madison \\ kbponto@wisc.edu}
%\vspace{8pt}

%\cvmembers{Honorable Mention, McPherson Eye Research Institute Best Student Presentation 2014 \vspace{6pt}\\
%BACTER Research Fellow \vspace{6pt} \\
%NASA Space Grant Scholar}{Best Poster, IEEE SciVis 2013 \vspace{16pt}\\Invited Participant, IEEE VIS Doctoral Colloquium 2013 \vspace{6pt}\\
%Four-time University of Washington Dean's List member}

%\cvlistitem{Boundary Value Problems}
%\cvlistitem{Numerical Analysis}
%\cvlistitem{Parallel Computing}
\end{document}
